Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Debug

where:

- $$p_i \ \text{represents the probability of support for candidate i at a specific date.}$$
- $$\beta_0 \ \text{is the intercept, representing baseline support.}$$
- $$\beta_1 \ \text{captures changes in support over time (date effect).}$$
- $$\beta_2 \ \text{is a categorical variable accounting for each candidate.}$$

@@

>>>>>>> cadfff05ead6aebff23ab03f96847c7f519121a6
# Idealized Methodology

>>>>

where:
- $$p_i \ \text{represents the probability of support for candidate i at a specific date.}$$
- $$\beta_0 \ \text{is the intercept, representing baseline support.}$$
- $$\beta_1 \ \text{captures changes in support over time (date effect).}$$
- $$\beta_2 \ \text{is a categorical variable accounting for each candidate.}$$

@@
